On Logic Embeddings and G\"odel's God

### 2015-03-01 Papers/2014/WADT/WADT-4pages.tex
Improve another sentence.

There is little related work~\cite{oppenheimera11,rushby13}, and this
focuses solely on the comparably simpler, original ontological
argument by Anselm of Canterbury.  These works do not achieve the
close correspondence between the original formulations and the formal
encodings that can be found in our approach and they also do not reach
the same degree of proof automation.

>>>>

There have been few related works~\cite{oppenheimera11,rushby13}, 
and they have
focused solely on the comparably simpler, original ontological
argument by Anselm of Canterbury. These works do not achieve the
close correspondence between the original formulations and the formal
encodings that can be found in our approach and they also do not reach
the same degree of proof automation.
